A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
updated language counts and pie chart

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 2651 bilingual turkers}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
IGNORE TABLE& WILL FIX SOON&\\
&\# languages&\# Turkers\\
\hline
No languages&0&2555\\
One language&1&2651\\
Multiple languages&2&684\\
&3&94\\
&4&23\\
&5&7\\
&6&8\\
&7&4\\
&8&1\\
&9&2\\
&10&3\\
&15&1\\
\hline\hline
\end{tabular}
\label{numlangs-tab}\\
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 3154 bilingual turkers}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
&\# languages&\# Turkers\\ \hline
No languages&0&1801\\
One language&1&3154\\
Multiple languages&2&243	\\
&3&49\\
&4&12\\
&5&9\\
&6&5\\
&7&2\\
&8&1\\
&9&2\\
&10&2\\
&15&1\\
\hline\\hline
\end{tabular}
\label{numlangs-tab}
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
